---
title: "Introductory Resources on Multilevel Modeling"
author: "Kate Petrova"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: yes
    toc_depth: 3
    toc_float:
      collapsed: false
editor_options: 
  markdown: 
    wrap: 72
bibliography: references.bib
---

```{r setup, echo = FALSE, message=FALSE, warning=FALSE}
if(!suppressWarnings(require(pacman))){install.packages("pacman");library("pacman")}
p_load(webshot)
```

## Introductory resources on multilevel modeling {style="color: dark gray"}

### How to use this document?

Hello and welcome to ...

### Review of linear regression

...

#### Readings

+-------------+--------------------------------------------------------+
| *pp. 1-21*  | Winter, B. (2013). *Linear models and linear mixed     |
|             | effects models in R with linguistic applications*.     |
|             | <https://doi.org/10.48550/ARXIV.1308.5499>             |
+-------------+--------------------------------------------------------+
|             |                                                        |
+-------------+--------------------------------------------------------+
|             |                                                        |
+-------------+--------------------------------------------------------+
|             |                                                        |
+-------------+--------------------------------------------------------+

### Introduction to multilevel modeling

...

#### Visual introduction to hierarchical models

```{r visual intro, echo=FALSE}
knitr::include_url("http://mfviz.com/hierarchical-models/")
```

#### Multilevel modeling in R

```{r modeling in r, echo = FALSE}
knitr::include_url("https://m-clark.github.io/mixed-models-with-R/ ")
```

#### Readings

+-------------+--------------------------------------------------------+
| Chapters 2  | Raudenbush, S. W., & Bryk, A. S. (2002). *Hierarchical |
| & 4         | linear models: Applications and data analysis          |
|             | methods*. (Vol. 1). Sage.                              |
+-------------+--------------------------------------------------------+
|             |                                                        |
+-------------+--------------------------------------------------------+
|             |                                                        |
+-------------+--------------------------------------------------------+
|             |                                                        |
+-------------+--------------------------------------------------------+
