---
title: Introductory resources for multilevel modeling
author: "Kate Petrova"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: yes
    toc_depth: 3
    toc_float:
      collapsed: false
editor_options: 
  markdown: 
    wrap: 72
bibliography: references.bib
---

```{r setup, echo = FALSE, message=FALSE, warning=FALSE}
if(!suppressWarnings(require(pacman))){install.packages("pacman");library("pacman")}
p_load(webshot)
```

### How to use this document?

Hi there! This document was designed to serve as a loosely-organized
collection of introductory resources[^1] on multilevel modeling.

[^1]: Note: *You can find all texts in the RA resources -> Multilevel
    modeling folder on the Google Drive.*

To get a firm grasp on multilevel modeling, it is critical to understand
the ins-and-outs of the general linear model. For this reason, the first
section contains a collection of resources on linear regression.

The subsequent section links to a variety of introductory resources on
multilevel modeling. The resources were selected to provide both
conceptual foundations as well as to teach you to implement multilevel
modeling in R.

You will notice that some of the readings, videos, and other resources
go over the same information, so you might be tempted to skip over the
parts that seem repetitive. However, in my experience, mastery of
multilevel modeling (and many other statistical techniques more
generally) comes from repetition. Exposing yourself to different ways of
explaining the same information will help sharpen your understanding of
the key concepts and procedures and teach you how to flexibly *reason*
about multilevel modeling rather than simply memorizing definitions and
implementation steps. This ability is absolutely essential for you to be
able to work with a diverse range of data sets and avoid making mistakes
(the opportunities for which are never in short supply when it comes to
MLM!). For this reason, I recommend that you give your full attention to
all resources and revisit them frequently as you continue with your
learning.

Best of luck with your learning! I hope you find it both engaging and
rewarding.

### Review of linear regression

#### Correlation refresher

Begin by reading [this brief
chapter](https://stats.libretexts.org/Bookshelves/Applied_Statistics/Book%3A_An_Introduction_to_Psychological_Statistics_(Foster_et_al.)/12%3A_Correlations)
on correlations in the open textbook by Garett Foster.

Play around with the interactive tool below, paying particular attention
to how the correlation (r), shared variance (R^2^), and the visual
representations of the two change as you drag, add, and remove data
points.

```{r variance shared, echo = FALSE}
knitr::include_url("https://rpsychologist.com/correlation/")
```

#### Linear regression

Now that you have refreshed your memory on correlations, read this
*excellent* chapter on regression fundamentals by Rex Kline:

+------------+------------------------------------------------+
| pp. 25-41  | **Chapter 2: Regression Fundamentals** in      |
|            | Kline, R. B. (1998). Structural equation       |
|            | modeling. *New York: Guilford*.                |
+============+================================================+
+------------+------------------------------------------------+

#### Just for fun

```{r spurious correlations, echo = FALSE}
knitr::include_url("http://www.tylervigen.com/spurious-correlations")
```

### Introduction to multilevel modeling

#### Visual introduction to hierarchical models

```{r visual intro, echo = FALSE}
knitr::include_url("http://mfviz.com/hierarchical-models/")
```

Check out [this brief
video](https://www.youtube.com/watch?v=FCcVPsq8VcA&t=6s) by Tom Reader
for more on fixed and random effects.

#### Understanding different types of nested data

+--------------+-----------------------------------------------------+
| **Chapters 2 | Raudenbush, S. W., & Bryk, A. S. (2002).            |
| & 4**        | *Hierarchical linear models: Applications and data  |
|              | analysis methods*. (Vol. 1). Sage.                  |
+--------------+-----------------------------------------------------+
| **Chapter    | Singer, J. D., Willett, J. B., & Willett, J. B.     |
| 2**          | (2003). *Applied longitudinal data analysis:        |
|              | Modeling change and event occurrence*. Oxford       |
|              | university press.                                   |
+--------------+-----------------------------------------------------+

#### To center or not to center predictors?

```{r centering, echo = FALSE}
knitr::include_url("https://philippmasur.de/2018/05/23/how-to-center-in-multilevel-models/")
```

#### Multilevel modeling in R

```{r modeling in r, echo = FALSE}
knitr::include_url("https://m-clark.github.io/mixed-models-with-R/")
```
